Review: The Prevalence of Adaptive Introgression in Crop Histories

### 2018-06-26 paper.tex
edits to adaptation section

Research has so far shown that adaptive crop-wild introgression has played a significant role during domestication and dispersal of multiple important crops.
However, the dynamics of this process are not yet fully understood and many questions remain:

\subsection*{Do geographic patterns of introgression inform our understanding of adaptation?}
Conservation of the genomic architecture of introgression across individuals,  between populations, and across landscapes can help illuminate whether introgression is, in fact, adaptive.
For example, if an introgressed chromosomal region is conserved across a broad ecogeographic region, this suggests it may impart adaptation to general environmental or climatic variables.
On the other hand, if genetic architectures of introgression are conserved across individuals within a population but not across populations in the region, this suggests much more local selective pressures.
Highly variable introgression across individuals would be more consistent with random gene flow than adaptation.
Finally, introgression at genomic loci showing environmental association and/or a role in disease/pest resistance can be particularly suggestive of adaptive significance.

\subsection*{Over what timescales and in what genomic regions can we reliably detect adaptive introgression?}
Introgressed haplotypes are most easily detected with limited recombination post-hybridization.
Therefore, recent introgressions (limited meioses) or those occurring in low recombination regions such as centromeres or inversions are preferentially detected.
Moreover, since recombination will progressively degrade tracts of introgression, the genome-wide distribution of tract lengths based on a genetic map can be used to date introgression events (as in \cite{Poets2015}).
Mutation rate, effective population size, and strength of selection may also influence the rate of breakup of introgressed regions.

\subsection*{At what taxonomic scale does introgression occur?}
As species become substantially diverged, introgression can become maladaptive or impossible due to, for example, Dobzhansky-Muller incompatibilities and other pre- and post-zygotic barriers to hybridization.
Divergence time may therefore be a useful predictor of the possibility of gene flow between a particular wild relative and a domesticate.
Hybridization may also be limited between a crop and a particular wild relative due to demography. 
For instance, gene flow from a wild relative with a small long-term effective population size, and correspondingly high genetic load may not be favored by selection.
This effect has been observed in the case of Neanderthal introgression into humans, which was likely limited in extent and relegated largely to non-genic regions due to the high genetic load found within Neanderthal donor individuals \cite{harris2016genetic}.

>>>>

Research has so far shown that adaptive crop-wild introgression has played a significant role during domestication and dispersal of many important crops.
However, the scope and dynamics of this process are not yet fully described and remain unexplored in many systems.
In determining the extent and nature of adaptation due to introgression, several questions should be considered:

\subsection*{Do geographic patterns of introgression inform our understanding of adaptation?}
Conservation of the genomic architecture of introgression across individuals,  between populations, and across landscapes can help illuminate whether introgression is, in fact, adaptive.
For example, if an introgressed chromosomal region is conserved across a broad ecogeographic region, this suggests it may impart adaptation to more widespread environmental or climatic variables (\emph{e.g.}, cool temperatures at high elevation).
On the other hand, if genetic architectures of introgression are conserved across individuals within a population but not across populations in the region, this suggests much more local selective pressures (\emph{e.g.}, locally prevalent biotic pressures).
Highly variable introgression across individuals would be more consistent with random gene flow than adaptation.

\subsection*{Over what timescales and in what genomic regions can we reliably detect adaptive introgression?}
Introgressed haplotypes are most easily detected with limited recombination post-hybridization.
Therefore, recent introgressions (limited meioses) or those occurring in low recombination regions such as centromeres or inversions are preferentially detected.
Moreover, since recombination will progressively degrade tracts of introgression, the genome-wide distribution of tract lengths based on a genetic map can be used to date introgression events (as in \cite{Poets2015}).
Mutation rate, effective population size, and strength of selection on introgressed alleles may also influence the rate of breakup of introgressed chromosomal regions.
Detection of introgression will also be affected by the extent of divergence of donor taxa from a crop's wild progenitor; highly divergent introgressed haplotypes will be easier to identify.

\subsection*{At what taxonomic scale does introgression occur?}
As species become substantially diverged, introgression can become maladaptive or impossible due to, for example, Dobzhansky-Muller incompatibilities and other pre- and post-zygotic barriers.
Divergence time may therefore be a useful predictor of the possibility of gene flow between a particular wild relative and a domesticate.
Hybridization may also be limited between a crop and a particular wild relative due to demography. 
For instance, gene flow from a wild relative with a small long-term effective population size, and correspondingly high genetic load may not be favored by selection.
This effect has been observed in the case of Neanderthal introgression into humans, which was likely limited in extent and relegated largely to non-genic regions due to the high genetic load found within Neanderthal donor individuals \cite{harris2016genetic}.
